### 2011-11-06 doc/pldi2012/exec.tex

In this section we present the Legion execution model and show that
it is correct in that it is guaranteed to preserve the sequential
execution semantics of programs.  The correctness argument is
instructive in that the properties that ensure correctness are also
exploited in the implementation of the Legion high-level runtime
system to achieve high performance and highly distributed scheduling
of parallel tasks.

>>>>

%In this section we present the Legion execution model and show that
%it is correct in that it is guaranteed to preserve the sequential
%execution semantics of programs.  The correctness argument is
%instructive in that the properties that ensure correctness are also
%exploited in the implementation of the Legion high-level runtime
%system to achieve high performance and highly distributed scheduling
%of parallel tasks.

In section \ref{sec:type} we showed that the type system
only enables privileges to be passed with task calls.  Based on
this property of privileges we have claimed that our runtime
will be able to make local scheduling decisions.  In this
section we present the Legion execution model and show that
this property of scheduling preserves the sequential execution 
semantics of a program.  The correctness argument is
instructive in that the properties that ensure correctness are also
exploited in the implementation of the Legion high-level runtime
system to achieve high performance and highly distributed scheduling
of parallel tasks.
